---
title: "README"
author: "MG"
date: "7/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Author
María Guinda - mariaguinda@cherrypeaks.com

## Description

DSAIRM is an R package containing a set of simulation models (apps) that teach within-host infection dynamics and immune response modeling from a dynamical system perspective.

All models can be explored through a graphical user interface, no reading or writing code is required. Each app comes with documentation and instructions which teach important concepts of within-host and immune response modeling, and how to use simulation models to understand such concepts.

It is also possible to go beyond the graphical interface and directly access and modify all simulations to adapt them to your needs.


## Data



## Installation and Access App



## Platforms
This application was tested on Mac and Windows 10. 


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
